### 2018-07-14 latex/supplementaries.tex
Added new fig S2 - Birds based on Prum 2015

\textbf{The phylogenetic distribution of NamPRT and NNMT in birds and reptiles is scattered.}

>>>>

\textbf{The phylogenetic distribution of NamPRT and NNMT in birds and reptiles is scattered.} The phylogenetic distribution of birds and reptiles was adopted from \cite{Prum2015}. Families are marked with a green circle if they possess NamPRT without NNMT or a blue circle if they possess both NamPRT and NNMT.
